%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Mohsin Y Ahmed} & \href{mailto:mya5dm@virginia.edu}{mya5dm@virginia.edu}\\
   1643 Townwood Ct  & (+1)434-282-9705 \\
   Charlottesville VA, 22901
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Virginia}{Charlottesville, VA}
      {Ph.D in Computer Science}{January 2015 -- May 2019}
    \resumeSubheading
      {University of Virginia}{Charlottesville, VA}
      {Master of Computer Science}{August 2012 -- December 2014}
    \resumeSubheading
      {Bangladesh University of Engineering and Technology}{Dhaka, Bangladesh}
      {B.Sc in Computer Science and Engineering}{December 2004 -- October 2009}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intel Corporation}{Hillsboro, OR}
      {Software Engineering Intern}{July 2015 - December 2015}
    \resumeSubheading
      {University of Virginia}{Charlottesville, VA}
      {Graduate Research Assistant}{August 2012 - Present}  

    \resumeSubheading
      {Eastern University}{Dhaka, Bangladesh}
      {Lecturer of Computer Science}{August 2010 - August 2011}
      \begin{comment}
      \resumeItemListStart
        \resumeItem{Notifications}
          {Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, queuing and A/B testing. Built an internal app to run batch campaigns for marketing etc.}
        \resumeItem{Nostos}
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
        \resumeItem{Workflows}
          {Dataduct an open source workflow framework to create and manage data pipelines leveraging reusables patterns to expedite developer productivity.}
        \resumeItem{Data Collection}
          {Designed the internal survey and crowd sourcing platfowm which allowed for creating various tasks for crowd sourding or embedding surveys across the Coursera platform.}
        \resumeItem{Dev Environment}
          {Analytics environment based on docker and AWS, standardized the python and R dependencies. Wrote the core libraries that are shared by all data scientists.}
        \resumeItem{Data Warehousing}
          {Setup, schema design and management of Amazon Redshift. Built an internal app for access to the data using a web interface. Dataduct integration for daily ETL injection into Redshift.}
        \resumeItem{Recommendations}
          {Core service for all recommendation systems at Coursesa, currently used on the homepage and throughout the content discovery process. Worked on both offline training and online serving.}
        \resumeItem{Content Discovery}
          {Improved content discovery by building a new onboarding experience on coursera. Using this to personalize the search and browse experience. Also worked on ranking and indexing improvements.}
        \resumeItem{Course Dashboards}
          {Instructor dashboards and learner surveying tools, which helped instructors run their class better by providing data on Assignments and Learner Activity.}
      \resumeItemListEnd
      \end{comment}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Kinect Acoustic Localization and Activity Detection}
      {Real-time Kinect human skeletal tracking data was used to develop location based acoustic activity detection models. Sound direction-of-arrival was used to detect sound source among multiple human and machine sources. Location aware models for Speech Recognition using CMUSphinx tool and Speaker Identification using GMM models were developed. Work submitted to UbiComp '19.}
    \resumeSubItem{Smartphone Speaker Identification} {The collaborative speaker identification app exchanged training data among neighboring phones over Bluetooth to make and update event driven dynamic logistic regression classifiers. Built with Android and Weka toolkit. Published in EWSN '15.}
    \resumeSubItem{Test Strategy Optimization} {Developer and database designer for a software tool for test strategy optimization for various Intel products for Intel's internal usage. Used mathematical models (linear/quadratic regression) for predicting product DPM (defect per million). Developed with C\#, SQL server and syncfusion framework.}
    \resumeSubItem{Temperature Chamber Device Testing} {Wrote offline data analysis scripts for data collected from a temperature chamber for stress testing of a Intel device. The script was later widely used by the Intel team for several subsequent phases of data collection and analysis on device channel failure behavior. }
    \resumeSubItem{Step Detection with Inertial Sensors in Shoes} {Time series data from footsteps of various speed was collected by implanting a tri-axis accelerometer in a shoe. A dynamic threshold based algorithm was developed to infer footsteps from the sensor data which is adpative to different walking and running speeds. Work was accepted to be filed as a patent for Intel Corporation. }
    \resumeSubItem{Mood Detection from Speech for Distant Sources}
      {A set of distance agnostic speech features were experimentally found by their distortions to various distances and their f-scores for emotion detection. These features were used to train a SVM classifier for various mood detection from a public mood dataset (EmoDB). Synthetic reverberation were artificially added to the training data from a room impulse response simulator from the room's physical properties. Published in MobiQuitous '17.}
      
    \resumeSubItem{LAN Messenger}
      {Physical layer built using null modem, peer to peer data transmission with framing, flow control, error control using stop-wait protocol and CRC, network topology build-up and data transmission from one network to another using Link State Routing. Implemented with Java. }
    \resumeSubItem{Microcontroller Based Wireless Motorcar with Speed Control}
      {Using Atmel microcontroller platform and C, a PC controlled motor car was built. One-way communication protocol was implemented through a pair of 433 MHz radio transmitter-receiver. Speed control was handled using pulse-width modulation. }
    \resumeSubItem{Hardware Design Using Xilinx FPGA }
      {Sequential multiplier, VGA, pong video game, a simple processor. }
     \resumeSubItem{GPU Performance Benchmarking}
      {NVIDIA GEForce GTX 400 GPU performance benchmarking for k-means clustering, matrix multiplication and salt-pepper noise reduction from images. }
     
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}

  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      { Java, C/C++, C\#, Python, 80x86 assembly, Matlab, LaTex}
    
    \resumeSubItem{Machine Learning}
      { Weka, LibSVM, Matlab Neural Network, Tensorflow}
    
    \resumeSubItem{Hardware }
      { Atmel microcontroller, Xilinx FPGA, Arduino, Microsoft Kinect, Inertial sensors, Acoustic sensors}
    
  \resumeSubHeadingListEnd

\section{Patent}
\begin{itemize}[leftmargin=*]
    \item Mohsin Y Ahmed and Suraj Sindia. 2017. Technologies for pedometric sensing in footwear.  US Patent App. 15/187,113.
\end{itemize}

\section{Publications}
\begin{itemize}[leftmargin=*]
    \item Mohsin Y. Ahmed, Zeya Chen, Avinash Kalyanaraman, and John A. Stankovic. 2018.  LocoVocal: Indoors Real-Time, Location Adaptive, Human Acoustic Activity Detection. Submitted to UbiComp.
    \item Mohsin Y. Ahmed, Zeya Chen, Emma Fass, and John A. Stankovic. 2017.  Real Time Distant Speech Emotion Recognition in Indoor Environments. In MobiQuitous.
    \item Mohsin Y Ahmed, Sean Kenkeremath, and John Stankovic. 2015. Socialsense: A collaborative mobile platform for speaker and mood identification. In European Conference on Wireless Sensor Networks. Springer, 68–83.
    \item Asif Salekin, Zeya Chen, Mohsin Y Ahmed, John Lach, Donna Metz, Kayla De La Haye, Brooke Bell, and John A Stankovic. 2017. Distant Emotion Recognition. Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies 1, 3 (2017), 96.
    \item Sirajum Munir, Mohsin Ahmed, and John Stankovic. 2015.  Eyephy: Detecting dependencies in cyber-physical system apps due to human-in-the-loop. In proceedings of the 12th EAI International Conference on Mobile and Ubiquitous Systems: Computing, Networking and Services on 12th EAI International Conference on Mobile and Ubiquitous Systems: Computing, Networking and Services. ICST (Institute for Computer Sciences, Social-Informatics and Telecommunications Engineering), 170–179.
    \item Meiyi Ma, S Masud Preum, W Tarneberg, Mohsin Ahmed, Matthew Ruiters, and John Stankovic. 2016. Detection of runtime conflicts among services in smart cities. In Smart Computing (SMARTCOMP), 2016 IEEE International Conference on. IEEE, 1–10.
    \item Jessica Rayo, Brooke Bell, Mohsin Y Ahmed, Kayla de la Haye, John Lach, John A Stankovic, and Donna Spruijt-Metz. 2017. Monitoring and modeling family eating dynamics (m2fed): A system that detects family eating behaviors and moods in the home environment. In Psychosomatic Medicine, Vol. 79. Lippincott Williams \& Wilkins Two Commerce Sq, 2001 Market St, Philadelphia, PA 19103 USA, A7–A7.
    \item Amlan Ganguly, Mohsin Yusuf Ahmed, and Anuroop Vidapalapati. 2012. A denial-of-service resilient wireless NoC architecture. In Proceedings of the great lakes symposium on VLSI. ACM, 259–262.
    
\end{itemize}
%-------------------------------------------
\end{document}
